
### 2. Union of Two Events
# P(A) = 0.4, P(B) = 0.5, P(A ∩ B) = 0.3

```{r}
p_A <- 0.4
p_B <- 0.5
p_AandB <- 0.3
p_AorB <- p_A + p_B - p_AandB
p_AorB
```
### 3. Symmetric Difference of Events
# P(A) = 0.6, P(B) = 0.4, P(A ∩ B) = 0.2

```{r}
p_A <- 0.6
p_B <- 0.4
p_AandB <- 0.2
p_AorB <- p_A + p_B - p_AandB
p_sym_diff <- p_AorB - p_AandB
p_sym_diff
```


### 4. Addition Rule in Machine Maintenance
# P(A)=0.15, P(B)=0.10, P(A∩B)=0.05
```{r}
p_A <- 0.15
p_B <- 0.10
p_AandB <- 0.05
p_AorB <- p_A + p_B - p_AandB
p_AorB
```

### 5. Complement Rule in Reliability Analysis
# Probability of working without failure = 0.85
```{r}
p_work <- 0.85
p_fail <- 1 - p_work
p_fail
```

### 6. Symmetric Difference & Union in Quality Control
# P(A)=0.3, P(B)=0.4, P(A∩B)=0.1
```{r}
p_A <- 0.3
p_B <- 0.4
p_AandB <- 0.1
p_AorB <- p_A + p_B - p_AandB
p_sym_diff <- p_AorB - p_AandB
list(prob_sym_diff = p_sym_diff, prob_union = p_AorB)
```


### 7. Symmetric Difference in Inspection (Incomplete info)
# P(A)=0.20, P(B)=0.25, P(A∩B) not given
# General formulas:
# P(A Δ B) = P(A) + P(B) - 2P(A∩B)
# P(A ∪ B) = P(A) + P(B) - P(A∩B)
```{r}
cat("Symmetric difference: 0.20 + 0.25 - 2P(A∩B)\n")
cat("Union: 0.20 + 0.25 - P(A∩B)\n")
```

